### 2021-03-01 input/background.tex
structure

One could solve this issue by using a conflict-free replicated data
type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
require eventual delivery of messages to ensure convergence. All
processes need to receive, deliver, hence broadcast all
operations. Some processes may receive operations unnecessary to their
correct functioning, for these operations did not happen in their
locality.  One could also solve this issue by removing partitions that
were not advertised for a defined
time~\cite{hemmati2015namebased}. However, relying on physical timeout
could lead to either premature removals of partitions when they are
still operating; or slow convergence where processes believe they
belong to a partition that was removed (\TODO{plot ?}). In addition,
since timeouts imply a continuous maintenance of partitions, such
partitioning protocol incurs an overhead even in quiet contexts
without dynamic partitions.

\begin{problem}[Consistent partitioning]
  How to enable \emph{consistent} dynamic optimal partitioning in
  dynamic network using scoped flooding?
\end{problem}

@@

\begin{definition}[Partitions in asynchronous systems]
  Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
  \TODO{TODO}
\end{definition}

\begin{problem}[Consistent partitioning in AS]
  How to enable scoped flooding of objects in autonomous systems?
\end{problem}

\TODO{Next Section presents our approach that solves this problem
  statement by relying only on logical control information.}

>>>>

One could solve this issue by using a conflict-free replicated data
type (CRDT) for set data structures~\cite{shapiro2011crdts}. CRDTs
require eventual delivery of messages to ensure convergence. All
processes need to receive, deliver, hence broadcast all
operations. Some processes may receive operations unnecessary to their
correct functioning, for these operations did not happen in their
locality.  One could also solve this issue by removing partitions that
were not advertised for a defined
time~\cite{hemmati2015namebased}. \TODO{check distance-vector
  protocols.} However, relying on physical timeout could lead to
either premature removals of partitions when they are still operating;
or slow convergence where processes believe they belong to a partition
that was removed (\TODO{plot ?}). In addition, since timeouts imply a
continuous maintenance of partitions, such partitioning protocol
incurs an overhead even in quiet contexts without dynamic partitions.

\begin{problem}[\label{prob:intra}Consistent partitioning]
  How to enable \emph{consistent} dynamic optimal partitioning in
  dynamic network using scoped flooding?
\end{problem}

@@

\begin{definition}[Partitions in asynchronous systems]
  Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
  \TODO{TODO} \TODO{or multi-partitioning?}
\end{definition}

\begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
  How to enable scoped flooding of objects in autonomous systems?
\end{problem}

Next Section presents our approach that solves these scientific
problems by relying on logical control information only.

### 2021-03-01 input/proposal.tex
structure

In this section, we introduce \NAME, (\TODO{stands for}) a reactive
protocol for logical partitioning in autonomous systems the cost of
which actually depends on its usage: when the system becomes
quiescent, processes eventually converge to their respective partition
and do not require further communication afterwards.

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, generated traffic remains \TODO{low} using scoped
flooding. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another.

This section describes \NAME's components and algorithms. First, it
starts by detailing a logical partitioning protocol in static
network. Second, it extends such protocol to dynamic systems. Last, it
describes an optimization based on Bloom filter. \TODO{More more
  more. Thousands of pages paper it seems.}

\subsection{Dynamic partitions}

@@

At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:background}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

This allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, vectors of versions also ensure
termination, for corresponding add and delete messages cannot follow
each other in an infinite loop. In terms of traffic, this only
requires each \TODO{delete} message to piggyback a source identifier
and version number.

% \noindent \textbf{Second,} processes need to maintain a local view of
% their neighbors' partition.  Figure~\ref{fig:del} shows that
% \TODO{deletes} may not propagate properly to all processes in
% need. The path leading to processes delivering $add$ may be broken due
% to concurrent deliveries.  To solve this issue, each process is able
% to know with certainty that each of its neighbor does not need a
% delete (either because it is in another partition, or because another
% path exists from the source to this neighbor). \TODO{More, figures
%   etc.} In terms of traffic, this requires to acknowledge each message
% in a way or another (acknowledgement messages or included in each
% add-del message) using FIFO communication channels. The propagation of
% delete messages is limited to the partition it targets plus uncertain
% processes.

@@

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop up-to-date $\alpha$'s
    from reaching all processes that require it along the shortest path from $a$ to $c$.
    To solve this issue, we must guarantee
    the eventual removal of stale $\alpha$'s (see Figure~\ref{fig:proofB}).]
    {\input{input/figproofA.tex}}
    \hspace{10pt}
    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may stop $\delta$'s from reaching
    processes with targeted $\alpha$'s. To ensure correctness, $b$ must either
    deliver $\delta_d$, $\delta_d^{0.5}$, or another $\alpha$, as well as downstream processes
    that delivered $\alpha$ coming from $b$ such as $g$.]
    {\input{input/figproofB.tex}}
    \caption{\label{fig:proof}Dynamic partitioning leads to correctness issues due to
      staleness and ordering of operations.}
  \end{center}
\end{figure*}

\subsection{Dynamic networks}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\subsection{A last optimization}
\TODO{Carry information that is useless. such as order of processes in
  paths, and identities of processes themselves.} \TODO{Icarus for
  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
  know the dimension of networks and
  partitions~\cite{almeida2007scalable}}.

\subsection{Autonomous systems}

\begin{figure}
  \centering\input{input/figAS.tex}
  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
      issue not introduced in background}}
\end{figure}

@@

\begin{algorithm}
  \input{input/algoaaaa.tex}
  \caption{\label{algo:aaaa}Primitives for general purpose logical
    partitioning in dynamic systems.}
\end{algorithm}

@@

To ease the reasoning about inter-AS dynamic partitioning in dynamic
networks, \NAME runs an independant broadcast protocol for each
object, and for each rank of links.  \TODO{Not so easy\ldots}
\TODO{Write and describe algo.} \TODO{Overhead of separating things,
  slightly more memory, but traffic wise? slower ?}  \TODO{In the
  example, not only Process $b$ keeps $e_1$ as its best partition, but
  it keeps it for links of rank 0, and links of rank 1.}  When there
are no ranking in links, processes solely rely on
Algorithm~\ref{algo:adddelundo} for optimal partitioning.

>>>>

In this section, we introduce \NAME (\TODO{stands for}) and its
\underline{ex}tension \NAMEB, reactive protocols for logical
partitioning in autonomous systems the cost of which actually depends
on their usage: when the system becomes quiescent, processes
eventually converge to their respective partition and do not require
further communication afterward.

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, generated traffic remains \TODO{low} using scoped
flooding. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another. While \NAME is a general purpose logical
partitioning protocol for dynamic networks, \NAMEB further reduces
generated traffic in the context of inter-autonomous systems by
leveraging the hierarchical properties of such networks.

This section starts by describing \NAME's functioning by detailing its
operation to avoid inconsistent states due to ordering and staleness
of delivered messages. Then, it describes its extension \NAMEB that
builds multiple broadcast layers ordered using local knowledge only.
Finally, it ends with a complexity analysis of proposed protocols.

\subsection{Intra-autonomous system partitioning}

@@

\input{input/figproof.tex}

In this section, we aim at solving Problem Statement~\ref{prob:intra}
by proposing \NAME, a reactive logical partitioning protocol for
dynamic partitioning in dynamic networks.

\paragraph{Dynamic partitions.}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:background}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

This allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, this also ensure termination, for
corresponding add and delete messages cannot follow each other in
infinite loops.
% In terms of traffic, this only requires each message
% to piggyback a source identifier and version number.

@@

\TODO{Paths and \NAME synergize well, for paths tend to be smaller as the
number of sources increase in the system.}

\paragraph{Dynamic networks.}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\paragraph{A last optimization.}
\NAME makes extensive use of paths to enable deleting messages without
incrementing local counters. Messages carry their respective path and
processes detect when such messages have been looping when they carry
their identity (see Lines~\ref{line:notloopingA} and
\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
membership is all that matters, we propose to trade vectors of
identities for Bloom filters~\cite{almeida2007scalable} to improve on
generated traffic and
anonymity~\cite{whitaker2002forwarding}. Processes know with high
probability if they already received and forwarded each message
without knowing the identity of all processes that received it.  False
positive probability only incurs premature stopping of broadcast
messages and does not invalidate the delete of specific messages.

\subsection{Inter-autonomous system partitioning}

\begin{figure}
  \centering\input{input/figAS.tex}
  \caption{\label{fig:AS}Inter autonomous systems
    partitioning. \TODO{More about relative ordering of links at each
      process}}
\end{figure}

In this section, we aim at solving Problem Statement~\ref{prob:inter}
by proposing \NAMEB, an extension of \NAME, that enables dynamic
logical partitioning in inter-autonomous systems. It leverages
hierarchical properties of these networks to further improve on scoped
flooding.

@@

\begin{algorithm}
  \input{input/algoaaaa.tex}
  \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
    partitioning in inter-autonomous systems.}
\end{algorithm}

@@

To ease the reasoning about inter-AS dynamic partitioning in dynamic
networks, \NAME runs an independent broadcast protocol for each
object, and for each rank of links.  \TODO{Not so easy\ldots}
\TODO{Write and describe algo.} \TODO{Overhead of separating things,
  slightly more memory, but traffic wise? slower ?}  \TODO{In the
  example, not only Process $b$ keeps $e_1$ as its best partition, but
  it keeps it for links of rank 0, and links of rank 1.}  When there
are no ranking in links, processes solely rely on
Algorithm~\ref{algo:adddelundo} for optimal partitioning.
